### 2019-03-15 manuscript.rmd
added phylogeny inference folder

@@

```{r character_correlations, include=FALSE}
#PIC correlations with Rphylip
#C = sharedlogs[,c(-1,-3)] %>% .[which(!is.na(rowSums(.[,-1]))),]
C = sharedmatrix[,c(-1,-3)] %>% .[which(!is.na(rowSums(.[,-1]))),]
Cspecies = C$Species %>% as.character()
C = as.matrix(C[,-1])
rownames(C) = Cspecies
Ctree = drop.tip(ultram,which(!(ultram$tip.label %in% rownames(C))))
class(Ctree) = "phylo"
PICi = Rcontrast(tree=Ctree, X=C, path="phylip-3.695/exe", cleanup=TRUE)

@@

pGLSp_preylength = as.data.frame(matrix(nrow=ncol(PL_pruned_matrix[,-1]), ncol=1))
colnames(pGLSp_preylength) = "Copepod prey length"
row.names(pGLSp_preylength) = names(PL_pruned_matrix[,-1])
pGLS_PL_sign = pGLSp_preylength
pGLS_sign = pGLSp_preylength
for(i in 2:(ncol(PL_pruned_matrix)-1)){
  CH_I=as.numeric(PL_pruned_matrix[,i])
  names(CH_I) = PL_pruned_matrix$Species
  CH_I = CH_I[!is.na(CH_I)]
  CH_J=PL_pruned_matrix[,ncol(PL_pruned_matrix)]
  names(CH_J) = PL_pruned_matrix$Species
  CH_I = CH_I[!is.na(CH_I)]
  CH_I = CH_I[which(names(CH_I) %in% names(CH_J))]
  CH_J = CH_J[which(names(CH_J) %in% names(CH_I))]
  SE_I = PL_pruned_SEs[which(PL_pruned_SEs$Species %in% names(CH_I)),i]
  names(SE_I) = PL_pruned_SEs[which(PL_pruned_SEs$Species %in% names(CH_I)),1]
  SE_I = SE_I[match(names(CH_I), names(SE_I))]
  pgls_tree = drop.tip(ultram, which(!(ultram$tip.label %in% names(CH_I))))
  pg_data = as.data.frame(cbind(CH_I,CH_J)) %>% .[which(!is.na(rowSums(.))),]
  pgls.SEy(CH_I~CH_J, data=pg_data, tree = pgls_tree, se = SE_I) -> TTABLE
  pgls.SEy(CH_I~sample(CH_J, length(CH_J)), data=pg_data, tree = pgls_tree, se = SE_I) -> TTABLE_null
  TTABLE <- gls(CH_I ~ CH_J, correlation =  corBrownian(phy = pgls_tree), data = pg_data, method = "ML") %>% summary() %>% .$tTable %>% as.data.frame()
  TTABLE$`p-value`[2] -> pGLSp_preylength[i-1,1]
  if(pGLSp_preylength[i-1,1]<0.05){
     print(paste(rownames(pGLSp_preylength)[i-1],"Copepod prey length",pGLSp_preylength[(i-1),1],sep=" "))
     ValueIJ = TTABLE %>% .$Value %>% .[2]
     if(ValueIJ>0){pGLS_PL_sign[i-1,1] = "+"}
      else pGLS_PL_sign[i,1] = "-"
  }
}
write.csv(pGLSp_preylength, "PGLS_Pval_preylength.csv")
pGLS_PL_sign <- pGLS_PL_sign[which(rowSums(is.na(pGLS_PL_sign))!=ncol(pGLS_PL_sign)),which(colSums(is.na(pGLS_PL_sign))!=nrow(pGLS_PL_sign))]
write.csv(pGLS_PL_sign, "PGLS_SIGN_preylength.csv")
for(i in 2:ncol(PL_pruned_matrix)){
  plot(PL_pruned_matrix[,i], PL_pruned_matrix$`Copepod prey length (mm)`)
}

>>>>

#Cnidoband size evolution
cnisize = sharedmean_logs$cnidomic_index
names(cnisize) = sharedmean_logs$Species
treei = drop.tip(ultram, which(!(ultram$tip.label %in% names(cnisize))))
Phenogram(cnisize, as.data.frame(cnisize), treei)

@@

```{r character_correlations, include=FALSE}
#PIC correlations with Rphylip
#C = sharedlogs[,c(-1,-3)] %>% .[which(!is.na(rowSums(.[,-1]))),] ##Doesn't work
C = sharedmatrix[,c(-1,-3)] %>% .[which(!is.na(rowSums(.[,-1]))),]
Cspecies = C$Species %>% as.character()
C = as.matrix(C[,-1])
rownames(C) = Cspecies
Ctree = drop.tip(ultram,which(!(ultram$tip.label %in% rownames(C))))
class(Ctree) = "phylo"
PICi = Rcontrast(tree=Ctree, X=C, path="phylip-3.695/exe", cleanup=TRUE)

#PIC correlations by character, to get significance
PICp = as.data.frame(matrix(nrow=ncol(C), ncol=ncol(C)))
colnames(PICp) = colnames(C)
rownames(PICp) = colnames(C)
for(i in 2:ncol(sharedmean_logs)){
  Ci = sharedmean_logs[,i]
  names(Ci) = sharedmean_logs$Species
  Ci = Ci[!is.na(Ci)]
  for(j in 2:ncol(sharedmean_logs)){
    Cj = sharedmean_logs[,j]
    names(Cj) = sharedmean_logs$Species
    Cj = Cj[!is.na(Cj)]
    Cj = Cj[which(names(Cj) %in% names(Ci))]
    Ci = Ci[which(names(Ci) %in% names(Cj))]
    if(i!=j){
      ctree = drop.tip(ultram, which(!(ultram$tip.label %in% names(Cj))))
      class(ctree)<-"phylo"
      pic_i = pic(Ci, ctree)
      pic_j = pic(Cj, ctree)
      cor.test(pic_i, pic_j)$p.value %>% round3() -> PICp[i-1,j-1]
    }
    else PICp[i-1,j-1]<-NA
  }
}
write.csv(PICp, "PICcorrelations_pvalues.csv")

@@

pGLSp_preylength = as.data.frame(matrix(nrow=ncol(PL_pruned_matrix[,-1]), ncol=1))
colnames(pGLSp_preylength) = "Copepod prey length"
row.names(pGLSp_preylength) = names(PL_pruned_matrix[,-1])
pGLS_PL_sign = pGLSp_preylength
pGLS_sign = pGLSp_preylength
for(i in 2:(ncol(PL_pruned_matrix)-1)){
  CH_I=as.numeric(PL_pruned_matrix[,i])
  names(CH_I) = PL_pruned_matrix$Species
  CH_I = CH_I[!is.na(CH_I)]
  CH_J=PL_pruned_matrix[,ncol(PL_pruned_matrix)]
  names(CH_J) = PL_pruned_matrix$Species
  CH_I = CH_I[!is.na(CH_I)]
  CH_I = CH_I[which(names(CH_I) %in% names(CH_J))]
  CH_J = CH_J[which(names(CH_J) %in% names(CH_I))]
  SE_I = PL_pruned_SEs[which(PL_pruned_SEs$Species %in% names(CH_I)),i]
  names(SE_I) = PL_pruned_SEs[which(PL_pruned_SEs$Species %in% names(CH_I)),1]
  SE_I = SE_I[match(names(CH_I), names(SE_I))]
  pgls_tree = drop.tip(ultram, which(!(ultram$tip.label %in% names(CH_I))))
  pg_data = as.data.frame(cbind(CH_I,CH_J)) %>% .[which(!is.na(rowSums(.))),]
  pgls.SEy(CH_I~CH_J, data=pg_data, tree = pgls_tree, se = SE_I) -> TTABLE
  pgls.SEy(CH_I~sample(CH_J, length(CH_J)), data=pg_data, tree = pgls_tree, se = SE_I) -> TTABLE_null
  TTABLE <- gls(CH_I ~ CH_J, correlation =  corBrownian(phy = pgls_tree), data = pg_data, method = "ML") %>% summary() %>% .$tTable %>% as.data.frame()
  TTABLE$`p-value`[2] -> pGLSp_preylength[i-1,1]
  if(pGLSp_preylength[i-1,1]<0.05){
     print(paste(rownames(pGLSp_preylength)[i-1],"Copepod prey length",pGLSp_preylength[(i-1),1],sep=" "))
     ValueIJ = TTABLE %>% .$Value %>% .[2]
     if(ValueIJ>0){pGLS_PL_sign[i-1,1] = "+"}
      else pGLS_PL_sign[i,1] = "-"
  }
}
write.csv(pGLSp_preylength, "PGLS_Pval_preylength.csv")
#pGLS_PL_sign <- pGLS_PL_sign[which(rowSums(is.na(pGLS_PL_sign))!=ncol(pGLS_PL_sign)),which(colSums(is.na(pGLS_PL_sign))!=nrow(pGLS_PL_sign))]
write.csv(pGLS_PL_sign, "PGLS_SIGN_preylength.csv")
for(i in 2:ncol(PL_pruned_matrix)){
  plot(PL_pruned_matrix[,i], PL_pruned_matrix$`Copepod prey length (mm)`)
}
